---
title: "A Bayesian Network Risk Model for Predicting Survival Outcomes in Patients with Myeloma"
subtitle: "Kelly Quek and Chung H Kok"
output: html_document
date: "2023-05-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Extract survival score from Bayesian network model

In this tutorial, we will extract survival score using the example files provided. Load the necessary libraries.

```{r library, echo=TRUE, message=FALSE, warning=FALSE}

library(bnlearn)
library(kableExtra)
library(tidyverse)

```

## Reading the example data

Load the example data which contains 469 filtered pathways on 762 samples.

```{r data, echo=TRUE}
dat <- read.csv(file="../data/MMRF example with pathway activity score.csv", row.names = 1)
# head(dat)
```

Here is the list of 469 pathways. This list of pathways is also available in the repository.

```{r pathways, echo=TRUE, paged.print=TRUE}

pwy <- data.frame(pathways=names(dat))

pwy %>% head(5) %>%
  kbl() %>%
  kable_minimal()

```

## Load the survival model

Once we have the cancer hallmark pathways signature or activity score for each sample, we can load the Bayesian network myeloma survival model.

```{r load_model, echo=TRUE}

model <- readRDS(file="../database/BN_myeloma_survial_model.rds")

```

## Extract survival score

The model will predict the survival score on this provided example dataset based on the pathway signature score.

```{r prediction, echo=TRUE, paged.print=TRUE}

pred_score = data.frame(SampleID=rownames(dat), 
                        survival_score=predict(model, c("Vital_disease_status"), dat[, 1:dim(dat)[2]]))

head(pred_score) %>%
  kbl() %>%
  kable_minimal()

```
